---
title: "Using BiocHubsIngestR"
author: "Alexandru Mahmoud"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using BiocHubsIngestR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The `BiocHubsIngestR` package provides functionality for uploading data to temporary S3 endpoints created by the Bioconductor Hubs Ingest stack using the AWS SDK for R (`paws`). Before proceeding with data upload, you must:

1. Have an S3 ingestion endpoint generated by a Bioconductor admin
2. Receive access credentials (username and password) from the admin

## Authentication

First, set up your credentials using the `auth()` function. This will configure the necessary AWS credentials and endpoint for the S3 client:

```{r eval=FALSE}
# Replace with your actual credentials provided by the admin
BiocHubsIngestR::auth(username = "your_username", password = "your_password")
```

## Uploading Data

Once authenticated, you can upload either individual files or entire directories:

```{r eval=FALSE}
# Upload a single file
BiocHubsIngestR::upload("path/to/your/file.txt")

# Upload an entire directory
BiocHubsIngestR::upload("path/to/your/data/directory")
```

The `upload()` function will create a bucket if it doesn't exist and handle the transfer of files to the S3 endpoint. Progress messages will be displayed during the upload process.

## Implementation Details

The package uses the `paws` SDK to interact with S3-compatible storage. The endpoint configuration is handled automatically when you authenticate with your credentials. All uploads are performed using the S3 client configured specifically for your assigned endpoint.

## Important Notes

1. After completing your data upload, notify the Bioconductor admin you are coordinating with.
2. Once you inform the admin that the upload is complete, the endpoint will be locked for processing and no further uploads will be possible.
3. Make sure all your data is uploaded completely before notifying the admin.

For questions or issues, please contact the Bioconductor team or open an issue on the package's GitHub repository.
